---
title: "Summer Session"
---

# {.tabset}

## Overview

<!--
- Performance Review Worksheet ([.gdoc][prwgdoc])
- Evaluation Sign-Up Sheet ([.gdoc][esus1])
-->

Welcome to Advanced GIS Consulting Summer Program!

You are now a team member in our organization that specializes in providing a variety of geospatial solutions to some very esteemed clients.

Watch the introductory video by our head consultant, Dr. Tyler W. Davis.

<div style="text-align:center">
<iframe width="560" height="315" src="https://www.youtube.com/embed/f_3EM89Zynw" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
</div>

As a part of this summer program, you are expected to:

* develop advanced geospatial skills and techniques
* work collaboratively with your team to solve the main three projects along with any "special works" that may come up while you are here
* maintain a log/report that outlines *everything* you do (including any research, development, analysis, and collaboration) and approximately how long it took you to do it
* communicate with your supervisor and team members using remote/web-based technology
* meet with your supervisor three times:
    1. during the first week to overview the Performance Review Worksheet and the expectations for the Performance Accomplishments;
    2. during or just following the third week to report on your progress; and
    3. at or near the end of the summer session for the oral evaluation of your performance accomplishments
* ask questions and make mistakes
* uphold professionalism in everything you do

[esus1]: #
[prwgdoc]: #

### Getting Started Checklist

- Join "AdvGIS - Su2020" GroupMe chat
- Join "AdvGIS - Summer 2020" ArcGIS Online group
- Join "adv-gis" GitHub team (*notify your instructor of your GitHub username*)
- Read the syllabus/watch the video
- Read Ben Balter's ["15 rules for communicating at GitHub"](https://ben.balter.com/2014/11/06/rules-of-communicating-at-github/)
- Subscribe to the [Advanced GIS | Summer 2020 YouTube Playlist](https://www.youtube.com/playlist?list=PLbIkNQKCuzMPKtzAT_cfdge7JYdebm42A)
- Respond to the discussion "Introduce Yourself" found on GitHub
- Respond to the first discussion topic on GitHub
- Review the Performance Accomplishments and Performance Review Worksheet (*shared with you via Google Drive*)

```{r shark, child = 'project-shark.Rmd'}
```

```{r electioneering, child = 'project-electioneering.Rmd'}
```

```{r geofencing, child = 'project-geofencing.Rmd'}
```
