---
title: "Summer Session"
---

# {.tabset}

## Overview

- Performance Review Worksheet ([.gdoc][prwgdoc])
- Evaluation Sign-Up Sheet ([.gdoc][esus1])

Welcome to Advanced GIS Consulting!

You are now a team member in our organization that specializes in providing a variety of geospatial solutions.
As a part of this summer internship program, you are expected to:

* develop advanced geospatial skills and techniques
* work collaboratively with your team to solve the main three projects along with any "special works" that may come up while you are here
* maintain a log/report that outlines *everything* you do (including any research, development, analysis, and collaboration) and approximately how long it took you to do it
* communicate with your supervisor and team members using remote/web-based technology
* meet with your supervisor three times:
    1. during the first week to overview the Performance Review Worksheet and the expectations for the Performance Accomplishments;
    2. during or just following the third week to report on your progress; and
    3. at or near the end of the summer session for the oral evaluation of your performance accomplishments
* ask questions and make mistakes
* uphold professionalism in everything you do

[esus1]: #
[prwgdoc]: #


```{r shark, child = 'project-shark.Rmd'}
```

```{r electioneering, child = 'project-electioneering.Rmd'}
```

```{r geofencing, child = 'project-geofencing.Rmd'}
```
