---
title: "Summer Session"
---

# {.tabset}

## Overview

- Performance Review Worksheet ([.gdoc][prwgdoc])
- Evaluation Sign-Up Sheet ([.gdoc][esus1]) **&#8592; please sign up for Week 1 meeting**

Welcome to Advanced GIS Consulting Summer Program!

You are now a team member in our organization that specializes in providing a variety of geospatial solutions to some very esteemed clients.

Watch the introductory video by our head consultant, Dr. Tyler W. Davis.

<div style="text-align:center">
<iframe width="560" height="315" src="https://www.youtube.com/embed/f_3EM89Zynw" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
</div>

As a part of this summer program, you are expected to:

* develop advanced geospatial skills and techniques
* work collaboratively with your team to solve the main three projects along with any "special works" that may come up while you are here
* maintain a log/report that outlines *everything* you do (including any research, development, analysis, and collaboration) and approximately how long it took you to do it
* communicate with your supervisor and team members using remote/web-based technology
* meet with your supervisor three times:
    1. during the first week to overview the Performance Review Worksheet and the expectations for the Performance Accomplishments;
    2. during or just following the third week to report on your progress; and
    3. at or near the end of the summer session for the oral evaluation of your performance accomplishments
* ask questions and make mistakes
* uphold professionalism in everything you do

[esus1]: https://docs.google.com/spreadsheets/d/1tmNlCMUDELGg9N_5LxvcmteH1YhipkrMT8zSxfvJkHg/edit?usp=sharing
[prwgdoc]: https://docs.google.com/document/d/1bOJ72vt2eomMd6ffNRbZlSVFac4CIAd7M9fYuu68-ws/edit?usp=sharing

### Getting Started Checklist
I have simplified the checklist into a [GitHub issue](https://github.com/cga-wm/advgis-beta/issues/3).
I will update it as we go along.
Most content will be delivered via our [YouTube Playlist](https://www.youtube.com/playlist?list=PLbIkNQKCuzMPKtzAT_cfdge7JYdebm42A), so please subscribe for notifications.
Please feel free to comment on the issue with questions, requests, or clarifications.

### Lectures

* [Geoethics](lectures/geoethics/index.html)


```{r shark, child = 'project-shark.Rmd'}
```

```{r electioneering, child = 'project-electioneering.Rmd'}
```

```{r geofencing, child = 'project-geofencing.Rmd'}
```
