---
title: "Summer Session"
---

# {.tabset}

## Overview

- Performance Review Worksheet ([.gdoc][prwgdoc])
- Evaluation Sign-Up Sheet ([.gdoc][esus1]) **&#8592; please sign up for Week 1 meeting**

Welcome to Advanced GIS Consulting Summer Program!

You are now a team member in our organization that specializes in providing a variety of geospatial solutions to some very esteemed clients.

Watch the introductory video by our head consultant, Dr. Tyler W. Davis.

<div style="text-align:center">
<iframe width="560" height="315" src="https://www.youtube.com/embed/f_3EM89Zynw" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
</div>

As a part of this summer program, you are expected to:

* develop advanced geospatial skills and techniques
* work collaboratively with your team to solve the main three projects along with any "special works" that may come up while you are here
* maintain a log/report that outlines *everything* you do (including any research, development, analysis, and collaboration) and approximately how long it took you to do it
* communicate with your supervisor and team members using remote/web-based technology
* meet with your supervisor three times:
    1. during the first week to overview the Performance Review Worksheet and the expectations for the Performance Accomplishments;
    2. during or just following the third week to report on your progress; and
    3. at or near the end of the summer session for the oral evaluation of your performance accomplishments
* ask questions and make mistakes
* uphold professionalism in everything you do

[esus1]: https://docs.google.com/spreadsheets/d/1tmNlCMUDELGg9N_5LxvcmteH1YhipkrMT8zSxfvJkHg/edit?usp=sharing
[prwgdoc]: https://docs.google.com/document/d/1bOJ72vt2eomMd6ffNRbZlSVFac4CIAd7M9fYuu68-ws/edit?usp=sharing

***

### Getting Started Checklist
I have simplified the checklist into a [GitHub issue](https://github.com/cga-wm/advgis-beta/issues/3).
I will update it as we go along.
Most content will be delivered via our [YouTube Playlist](https://www.youtube.com/playlist?list=PLbIkNQKCuzMPKtzAT_cfdge7JYdebm42A), so please subscribe for notifications.
Please feel free to comment on the issue with questions, requests, or clarifications.

***

### Important Links:

* [Discussion Board](https://github.com/orgs/cga-wm/teams/adv-gis/discussions)
* [Issue Tracker](https://github.com/cga-wm/advgis-beta/issues)
* [Video Playlist](https://www.youtube.com/playlist?list=PLbIkNQKCuzMPKtzAT_cfdge7JYdebm42A)
* [ArcGIS Docs](https://doc.arcgis.com/en/)

***

### Keeping on Track
I will be posting lots of videos, lessons, lectures, materials, datasets, and discussions.
To avoid everything from overwhelming you, I suggest that you create your own checklist of tasks.
I've created the "Getting Started Checklist" using GitHub's Issue Tracker; feel free to copy this list to begin your own.

In Markdown you can create task lists using the following syntax:

```md
- [x] Completed task
- [ ] Todo item
- [ ] Todo item
```

You can add new items and check them off your list at any time.
I suggest putting your initials in the title and assigning the Issue to yourself, so we know who's it is.

In general, I recommended that you spend the first three weeks working on Project A and/or Project B.
There will be a fairly steep learning curve to all the new tools, syntax, and programming language.

This will leave the last two weeks for working on Project C, which extends our lessons from programming for GIS to programming GIS for the web.

You may, of course, work on all three projects simultaneously, but in terms of allocating your time, I still suggest about 60% be spent on Projects A/B and 40% spent on Project C.

***

### Lectures

* [Geoethics](lectures/geoethics/index.html)

***

### Resources

#### AGOL

* https://www.arcgis.com/index.html
* [W&M access to ArcGIS Online](https://youtu.be/x07Xyoe0d2k)
* [What can I add to ArcGIS Online?](https://doc.arcgis.com/en/arcgis-online/reference/supported-items.htm)
* [Documentation and resources](https://www.esri.com/en-us/arcgis/products/arcgis-online/resources)

#### ArcGIS Pro

* [Installation instructions (for Windows users only)](https://www.wm.edu/as/cga/arcgis-licensing/index.php)
* Access through VDI on Windows (see [here](https://youtu.be/pZh-fMoaV54)) or on Mac (see [here](https://youtu.be/lG43GtH1Ta4))
* [Documentation and resources](https://www.esri.com/en-us/arcgis/products/arcgis-pro/resources)

#### QGIS

* [Installation instructions](https://www.qgis.org/en/site/forusers/index.html)
* Access through VDI on Windows (see [here](https://youtu.be/pZh-fMoaV54)) or on Mac (see [here](https://youtu.be/lG43GtH1Ta4))
* [Documentation and resources](https://www.qgis.org/en/docs/index.html)

#### Notebooks

* [Getting Started With Notebooks (ArcGIS Online)](https://doc.arcgis.com/en/arcgis-online/get-started/components-of-the-notebook-editor.htm)
* [Basic writing and formatting (GitHub)](https://docs.github.com/en/github/writing-on-github/basic-writing-and-formatting-syntax)

#### Python

* [The Hitchhiker's Guide to Python](https://python-guide.readthedocs.io/en/latest/)
* [Basics of Python & arcpy](https://www.udemy.com/python-arcpy1/)
* [Automate the Boring Stuff with Python](https://automatetheboringstuff.com/)
* [Python for ArcGIS](https://doi.org/10.1007/978-3-319-18398-5). Tateosian (2015).
* [Geoprocessing with Python; Ch. 2](https://livebook.manning.com/book/geoprocessing-with-python/chapter-2/1). Garrard (2016).
* [Creating a new Python toolbox](https://pro.arcgis.com/en/pro-app/arcpy/geoprocessing_and_python/creating-a-new-python-toolbox.htm)

#### Geoethics
* [International Association for Promoting Geoethics (IAPG)](http://www.geoethics.org/)
* [Definition of Geoethics (IAPG)](http://www.geoethics.org/definition)
* [The Meaning of Geoethics, Peppoloni & Di Capua (2015)](http://www.geoethics.org/articles-geoethics#comp-ijx091vi)
* [The Emerging Field of Geoethics, Bobrowsky et al. (2017)](http://www.geoethics.org/articles-geoethics#comp-jjfx3jvm)
* Nguyen et al. (2017). Smartphone-based "geofencing" to ascertain hospitalizations. *Circ Cardiovasc Qual Outcomes* 10(3). doi: [10.1161/CIRCOUTCOMES.116.003326](https://dx.doi.org/10.1161/CIRCOUTCOMES.116.003326)
* [Carman (2017). Snapchat advertisers can now track whether custom geofilters get you to buy their product. The Verge](https://www.theverge.com/2017/4/13/15289178/snapchat-ad-tracking-snap-to-store-geofilters)
* [Patino (2020). Why Asian countries have succeeded in flattening the curve. Citylab](https://www.citylab.com/life/2020/03/coronavirus-stay-at-home-order-lockdown-social-distancing/608857/)
* [Schuppe (2020). Google tracked his bike ride past a burglarized home. That made him a suspect. NBC News](https://www.nbcnews.com/news/us-news/google-tracked-his-bike-ride-past-burglarized-home-made-him-n1151761)

#### Vlog / Podcast Tools
* [Audacity](https://www.audacityteam.org/) - an open-source cross-platform audio software.
* [Blender](https://www.blender.org/) - an open-source video editor/renderer.
* [iSkySoft](https://www.iskysoft.com/video-editing/combine-audio-and-video.html)


```{r shark, child = 'project-shark.Rmd'}
```

```{r electioneering, child = 'project-electioneering.Rmd'}
```

```{r geofencing, child = 'project-geofencing.Rmd'}
```
